Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-15 inc/extension/initial_conditions/initial_conditions.tex
grammar (Dan Brajkovic++)

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_{max}N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a Gaussian, we can determine $\sigma_z(0)$, the initial longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the initial photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{max} $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to separate from one another.

>>>>

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_{max}N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a Gaussian, we can determine $\sigma_z(0)$, the initial longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however, unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the initial photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{max} $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to separate from one another.
